---
title: "Favorite Code Chunks"
author: "Holly Crowder"
date: '2024-06-27'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
df<- mtcars
```

```{r}


```

```{r}

```


## %nin% 

put this at the top of your code so that you can use %nin% 
```{r %nin%}
`%nin%` = Negate(`%in%`)
```

##Filtering data
%>% require tidyverse 
```{r}
library(tidyverse)
mylist <- c("setosa")
iris<-iris%>%
  filter(Species %in% mylist & Petal.Length >= 1.5)
head(iris)
```


##grouping 

This will print the mean mpg per cyl 
```{r, echo=TRUE, results='hide'}
mean_mpgs<- df%>% 
  group_by(cyl)%>%
  summarise(mean_mpg = mean(mpg))
```
now we can compare each vs the expected value
```{r}
df$above_avg_mpg<- df%>% 
  group_by(cyl)%>%
  case_when(mpg> mean_mpgs$mpg)
```

#use grouping to check data against a reference set 
```{r}

```




## DT::datatable
Makes a fully interactive data table in rmd documents with no extra work.
```{r datatable}
DT::datatable(df)
```
This is wonderful because you can selectively display certain columns, and limit how many rows it shows on each page
```{r datatable cols}
DT::datatable(df[,c(1:2,6)])
```
when you confine it to a fill container it will give you scrollbars automatically. Yoy can use the scrollY option to change the size. 
```{r fill.container}
options(DT.fillContainer = T)
DT::datatable(df, options = list(pageLength = 10,scrollY = "200px"))
```

