---
title: "Dicoms_on_Box"
author: "Holly Crowder"
date: '2024-06-26'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

###################
library(readr)
library(tidyverse)
library(DT)
###################
df2 <- read_csv("HoltonImageFiles_edit_hc.csv", col_names = c("FolderName", "ID", "Date", "Scan", "SeriesDescription", "Size","X","Y","Z","Instances"), 
                col_types = cols(Date = col_date(format = "%Y_%m_%d")))

df2$Date<-format(df2$Date, format = "%Y-%m-%d")
df2<-na.omit(df2)
# List of expected scans
required_series_desc <- c("Siemens_MPRAGE", 
                          "Siemens_MPRAGE_ND",
                          "ep2d_3.2mm_2Back", 
                          "gre_field_mapping_2Back_ND",
                          "gre_field_mapping_2Back")
care_about_sd<- c("Siemens_MPRAGE", 
                  "Siemens_MPRAGE_ND",
                  "Siemens_MPRAGE_2x2x2", 
                  "Siemens_MPRAGE_2x2x2_ND",
                  "ep2d_3.2mm_2Back", 
                  "gre_field_mapping_2Back_ND",
                  "gre_field_mapping_2Back")

today_date<- Sys.Date()
today_date<-as.character(today_date)
`%nin%` = Negate(`%in%`)

datalog2<- read_csv("datalog_2024_06_26.csv", 
                               col_types = cols(`Date of Scan` = col_date(format = "%m/%d/%Y")))
datalog2<- datalog2[,1:2]
colnames(datalog2)[1:2] <- c("Date","ID")
datalog2$Date<-format(datalog2$Date, format = "%Y-%m-%d")


check_series_desc <- function(df2, required_series_desc) {
  
  missing_df2 <- data.frame()
  
  # loop through each foldername
  for (i in unique(df2$FolderName)) {
    subset_df <- df2[df2$FolderName == i, ]
    
    present_sd <- subset_df$SeriesDescription
    
    # Find missing series descriptions
    missing_sd <- setdiff(required_series_desc, present_sd)
    
    # Append missing series descriptions to missing_df2
    if (length(missing_sd) > 0) {
      missing_sd_rows <- data.frame(ID = rep(i, length(missing_sd)),
                                    SeriesDescription = missing_sd,
                                    stringsAsFactors = FALSE)
      missing_df2 <- rbind(missing_df2, missing_sd_rows)
    }
  }
  
  # Return the combined missing descriptions data frame
  return(missing_df2)
}

df2_check<-df2%>%
  filter(SeriesDescription %in% care_about_sd)
sd = df2_check$SeriesDescription
df2_check$expected_instances = case_when(grepl("Siemens_MPRAGE_ND$",sd ) ~ 1,
                               grepl("Siemens_MPRAGE$", sd) ~ 1,
                               grepl("Siemens_MPRAGE_2x2x2$", sd) ~ 1,
                               grepl("Siemens_MPRAGE_2x2x2_ND$", sd) ~ 1,
                               grepl("ep2d_3.2mm_2Back$", sd) ~ 124,
                               grepl("gre_field_mapping_2Back_ND$", sd) ~ 1,
                               grepl("gre_field_mapping_2Back$", sd) ~ 1)

df2_check$expected_slices = case_when( grepl("Siemens_MPRAGE_ND$", sd) ~ 176,
                                         grepl("Siemens_MPRAGE$", sd) ~ 176,
                                         grepl("Siemens_MPRAGE_2x2x2$", sd) ~ 176,
                                         grepl("Siemens_MPRAGE_2x2x2_ND$", sd) ~ 176,
                                         grepl("ep2d_3.2mm_2Back$", sd) ~ 64,
                                         grepl("gre_field_mapping_2Back_ND$", sd) ~ 64,
                                         grepl("gre_field_mapping_2Back$", sd) ~ 64)

df2_check$expected_size = case_when( grepl("Siemens_MPRAGE_ND$", sd) ~ 22.53,
                                       grepl("Siemens_MPRAGE$", sd) ~ 22.53,
                                       grepl("Siemens_MPRAGE_2x2x2$", sd) ~ 5.63,
                                       grepl("Siemens_MPRAGE_2x2x2_ND$", sd) ~ 5.63,
                                       grepl("ep2d_3.2mm_2Back$", sd) ~ 46.62,
                                       grepl("gre_field_mapping_2Back_ND$", sd) ~ 0.38,
                                       grepl("gre_field_mapping_2Back$", sd) ~ 0.38)
df2_check$Date<- as.character(df2_check$Date)

df2_check$correctslice<- case_when(df2_check$X== df2_check$expected_slices ~ TRUE,
                                df2_check$X!=df2_check$expected_slices ~ FALSE)
df2_check$correctinstance <- case_when(df2_check$Instances==df2_check$expected_instances ~ TRUE,
                                       df2_check$Instances!=df2_check$expected_instances ~ FALSE)
df2_check$correctsize <- case_when(df2_check$Size==df2_check$expected_size ~ TRUE,
                                   df2_check$Size!=df2_check$expected_size ~ FALSE)

instance_errors<- df2_check%>% 
  filter(correctinstance==FALSE)
slice_errors<- df2_check%>%
  filter(correctslice==FALSE)
size_errors<-df2_check%>% 
  filter(correctsize==FALSE)
instance_errors_bySD<- df2_check%>% 
  group_by(FolderName,SeriesDescription)%>%
  filter(all(correctinstance==FALSE)|all(correctsize==FALSE)|all(correctslice==FALSE)) 

at_least_one_good<- df2_check%>% 
  group_by(FolderName,SeriesDescription)%>%
  filter(any(correctinstance==TRUE)) 

dates_good<- at_least_one_good %>%
  group_by(ID)%>%
  filter(Date %in% datalog2$Date)

date_bad<-df2_check %>%
  group_by(ID)%>%
  filter(Date %nin% datalog2$Date)
missing_entire_ses <- datalog2 %>%
  group_by(ID)%>%
  filter(Date %nin% df2_check$Date)

```

## R Markdown

This First Summary will indicate if any of the following were missing entirely: 

"Siemens_MPRAGE", 
"Siemens_MPRAGE_ND",
"ep2d_3.2mm_2Back", 
"gre_field_mapping_2Back_ND",
"gre_field_mapping_2Back"

```{r Missing Series, echo=FALSE}
missing_series_descriptions<- check_series_desc(df2, required_series_desc)
DT::datatable(missing_series_descriptions)
```

## Checking Instances

Here are all cases where a scan was present, but the number of instances were wrong. 

The following tables checked the following scans:
"Siemens_MPRAGE", 
"Siemens_MPRAGE_ND",
"Siemens_MPRAGE_2x2x2", 
"Siemens_MPRAGE_2x2x2_ND",
"ep2d_3.2mm_2Back", 
"gre_field_mapping_2Back_ND",
"gre_field_mapping_2Back"


```{r instance, echo=FALSE}


DT::datatable(instance_errors[,c(2:5,10,11)], options = list(pageLength = 10))

```
## Checking Slices

This table will show you any cases where the number of slices was wrong

```{r slices, echo=FALSE}
DT::datatable(slice_errors[,c(2:5,7,12)], options = list(pageLength = 10))

```

## Checking Size

This table will show you if the size was wrong
```{r, echo=FALSE}
DT::datatable(size_errors[,c(2:5,6,13)], options = list(pageLength = 10))
```

## Checking that every *collected* scan has at least one version that is correct
You'll notice that all the errors above were for the 2Back, this is expected, but I wanted to make sure all these participants had at least one that had the correct number.

This next table filters any IDs that did not have **at least one** fully-correct correct scan(provided that it was run in the first place). You want this to be empty. 
```{r, echo=FALSE}
DT::datatable(instance_errors_bySD[,c(2:5,14:16)], options = list(pageLength = 10))
```

## Checking that the dates match
This will display any cases where the date does not match our master spreadsheet
```{r, echo=FALSE}
DT::datatable(date_bad[,c(2:5)], options = list(pageLength = 10))
```

Lastly, here is the full table, complete with the helper columns that made this happen. 
```{r, echo=FALSE}
options(DT.fillContainer = T)
DT::datatable(df2_check, options = list(pageLength = 10,scrollY = "565px"))
```

```{r, echo=FALSE}

#write.csv(missing_series_descriptions, paste0("missing_series","_",today_date,".csv"))
#write.csv(df2_check, paste0("swith_helper_columns","_",today_date,".csv"))
```

